\textbf{How to measure maximally precise radial velocities from a set of spectra:\\ The time-independent spectrum case}

### 2019-08-09 paper/paper.tex
tweak

\keywords{
atmospheric effects
---
binaries: spectroscopic
---
methods: data analysis
---
methods: statistical
---
techniques: radial velocities
---
planets and satellites: detection
}

>>>>

\keywords{\raggedright
atmospheric~effects
---
binaries:~spectroscopic
---
methods:~data analysis
---
methods:~statistical
---
techniques:~radial~velocities
---
planets~and~satellites:~detection
}
